---
title: "Focus Colombia"
subtitle: "Recent Economic Developments and Forecasts"
author: "César Castro Rozo"
date: "Updated: July 21, 2017"
output: html_document
---

****

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

****
> This section presents the monthly updating forecasts for the GDP, inflation and monetary policy in Colombia. The forecasts are analyzed with time series techniques, especially Bottom-Up procedures in hierarchical structures. The methodology consider the idiosincracy of models at disaggregate level of the variables, with the advantage of including proper monthly indicators for each sector. The forecasts also include a scenario for the movements of one of the most important variable for the Colombian economy: the world oil price. The bottom of the section shows the expected key interest from the Central Bank, based on the Taylor rule.

****
See monthly reports in PDF (Spanish):\
 \
> [July 2017](7Julio17.pdf)\
> [June 2017](6Junio17.pdf)\
> [May 2017](5Mayo17.pdf)\
> [April 2017](4Abril17.pdf)\
> [March 2017](3Marzo17.pdf)\
> [February 2017](2Febrero17.pdf)\
> [January 2017](1Enero17.pdf)\
 \
> [December 2016](12Diciembre16.pdf)\
> [November 2016](11Noviembre16.pdf)\
> [October 2016](10Octubre16.pdf)\
> [September 2016](9Septiembre16.pdf)\
> [August 2016](8Agosto16.pdf)\
> [July 2016](7Julio16.pdf)

****
```{r datac, echo=FALSE, warning=FALSE, results='hide', message=FALSE}
libs <- c('readxl',            # leer excel
          'xlsx',              # escribir excel
          'forecast',          # arimas y predicciones
          'fanplot',           # hacer fanchart
          'matrixStats',       # agregación
          'xtable',            # hacer tablas
          'png',
          'dplyr',
          'dlm',
          'TSA',
          'knitr',
          'tsoutliers'         # outliers and intervention analysis
)
lapply(libs, require, character.only=T)

# GDP: errors
t.gerror <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "cuadro1")
t.gerror <- t.gerror[,2:5]
rownames(t.gerror) <- c('Agriculture', 'Mining', 'Industry', 'Household services',
                        'Construction', 'Trade', 'Transport', 'Financial',
                        'Services', 'Taxes', 'Private consumption', 
                        'Public consumption', 'Gross capital formation',
                        'Exports', 'Imports', 'TOTAL')

# GDP: annual supply
s.annual.table <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "cuadro2")
s.annual.table <- s.annual.table[,2:6]
rownames(s.annual.table) <- c('Agriculture', 'Mining', 'Industry', 
                              'Household services', 'Construction', 'Trade',
                              'Transport', 'Financial', 'Services', 'Taxes',
                              'TOTAL')

# GDP: demand
d.annual.table <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "cuadro4")
d.annual.table <- d.annual.table[,2:6]
rownames(d.annual.table) <- c('Private consumption', 'Public consumption',
                              'Gross capital formation', 'Exports', 'Imports',
                              'TOTAL')

# GDP: Figure
crecimiento <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "figura2")
crecactual <- ts(crecimiento[,2], start=c(2010,1), frequency=4)
crecprevio <- ts(crecimiento[,3], start=c(2010,1), frequency=4)

# Inflation: Figure
inflacion <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "figura3")
inflactual <- ts(inflacion[,2], start=c(2010,1), frequency=12)
inflprevio <- ts(inflacion[,3], start=c(2010,1), frequency=12)

# Inflation: errors
t.error.grupos <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "cuadro6")
t.error.grupos <- t.error.grupos[,2:5]
rownames(t.error.grupos) <- c('TOTAL', 'Core', 'FOOD', 'Processed food', 'Non-processed food', 'Non-energy industrial goods', 'Services', 'Energy')

# Inflation: forecasts
p.table <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "cuadro7")
p.table <- p.table[1:5,]

# Monetary policy
g <- read_excel("/Users/cesarcastrorozo/Dropbox/SpinOff/colombia/datos.xls",
                       "figura8")
g <- g[,2]
```

## GDP GROWTH: COLOMBIA

### Quarterly GDP growth: change in forecasts
```{r GDPfigure, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
plot(crecactual, type='l', col = 'firebrick', lwd = 4, ylim=c(1, 8),
     yaxt='n', ylab='', xlab='', main='year-on-year rates')
rect(time(crecactual)[(62-33):(62-33)],
     8,
     time(crecactual)[36:36],
     1, density=50, col = "pink")
abline(h=c(3, 4, 5, 6, 7), col='gray90')
abline(v = c(2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016),
       col='gray90')  # year line
lines(crecprevio, type='l', col="brown")    # -1: predicción de t-1
lines(crecactual, type='l', col = 'firebrick', lwd = 4)
axis(2, at = 1:8, las = 2, tcl = 0.5, labels = FALSE)
axis(4, at = 1:8, las = 2, tcl = 0.5)
legend(2014, 8, c("current quarter", "previous quarter"),
       lty = 1, cex=.9, bg='white', col = c('firebrick','brown'),
       lwd=c(4, 2), bty='n', text.col=c('firebrick','brown'))
```

****
### Innovations by sectors in the fourth quarter-2016
```{r GDPerror, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
colnames(t.gerror) <- c('Weights', 'Observed', 'Forecast', 'innovation')

t.error.growth <- xtable(t.gerror,
                         caption='year-on-year rates (Innovations are considered in relation with the forecasts estimated with information available at previous month)',
                         label='errores.growth', align=c('lc|cc|c'),
                          digits=1)

print(t.error.growth,
      booktabs=TRUE,
      size='scriptsize',
      caption.placement = "top",
      hline.after=c(-1, 0, 10, 15, 16),
      sanitize.text.function = function(x){x}, type="html")
```

****
### Dissagregated GDP Forecasts: Supply
```{r supply, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
colnames(s.annual.table) <- c('2013', '2014', '2015', '2016', '2017')

s.annual.table <- xtable(s.annual.table, caption='year-on-year rates',
                  label='s.annual.table', 
                  align=c('l','|','c','c','c','|','c','c'),
                  digits=1)
print(s.annual.table,
      booktabs=TRUE,
      size='scriptsize',
      hline.after=c(-1, 0, 10, 11),
      sanitize.text.function = function(x){x},
      caption.placement = "top", type="html")
```

****
### Dissagregated GDP Forecasts: Demand
```{r demand, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
colnames(d.annual.table) <- c('2013', '2014', '2015', '2016', '2017')

d.annual.table <- xtable(d.annual.table, 
                         caption='year-on-year rates',
                         label='d.annual.table', 
                         align=c('l','|','c','c','c','|','c','c'),
                         digits=1)
print(d.annual.table,
      booktabs=TRUE,
      size='scriptsize',
      hline.after=c(-1, 0, 5, 6),
      caption.placement = "top",
      type="html")
```

****
## INFLATION: COLOMBIA

### Monthly inflation: change in forecasts
```{r Ifigure, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
plot(inflactual, type='l', col = "slateblue4", lwd = 3, ylim=c(1.5, 9.5),
     yaxt='n', ylab='', xlab='', bty='n')
rect(time(inflactual)[(200-113):(200-113)],
     1.5,
     time(inflactual)[108:108],
     9.5, density=50, col = "lightsteelblue1")
abline(h=c(2, 4), col='firebrick')
abline(h=c(3, 5, 6, 7, 8, 9), col='gray90')
abline(v = c(2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016),
       col='gray90')  # year line
lines(inflprevio, type='l', col='slateblue', lwd=2)        # predicción de t-1
lines(inflactual, type='l', col = "slateblue4", lwd = 4)
axis(2, at = 1:9, las = 2, tcl = 0.5, labels = FALSE)
axis(4, at = 1:9, las = 2, tcl = 0.5)
legend(2010.5, 7.5, c("current month", "previous month"),
       lty = 1, cex=1.1, bg='white', col = c('slateblue4', 'slateblue'),
       lwd=c(4, 2), bty='n', text.col=c('slateblue4', 'slateblue'))
text(2016.5, 3, "monetary policy", cex = 1.1, col='firebrick')
box(col='dimgray')
```

****
### Innovations by sectors in June-2017
```{r Ierror, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
colnames(t.error.grupos) <- c('Weights', 'Observed', 'Forecast', 'Error')

t.error.grupos <- xtable(t.error.grupos,
                         caption='year-on-year rates (Innovations are considered in relation with the forecasts estimated with information available at previous month)',
                         label='table.error', align=c('lc|cc|c'), digits=1)

print(t.error.grupos,
      booktabs=TRUE,
      size='scriptsize',
      caption.placement = "top",
      hline.after=c(-1, 2, 8),
      sanitize.text.function = function(x){x}, type="html")
```

****
### Disaggregated Inflation Forecasts
```{r inflation, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
colnames(p.table) <- c(' ', 'TOTAL', 'CORE', 'Food',
                       'Manufactures', 'Services', 'Energy')
rownames(p.table) <- c('2013', '2014', '2015', '2016', '2017')

                       # '2016:1','2016:2','2016:3','2016:4',
                       # '2016:5','2016:6','2016:7','2016:8',
                       # '2016:9','2016:10','2016:11','2016:12',
                       # '2017:1','2017:2','2017:3','2017:4',
                       # '2017:5','2017:6','2017:7','2017:8',
                       # '2017:9','2017:10','2017:11','2017:12')

p.table <- xtable(p.table, caption='Year-on-year rates',
                  label='i.table', align=c('rr|cc|cccc'), digits=1)

print(p.table,
      booktabs=TRUE,
      size='scriptsize',
      # hline.after=c(-1, 5, 17, 29),
      caption.placement = "top",
      sanitize.colnames.function = identity, type="html", include.rownames=F
)
```

****
## SYSTEMATIC MONETARY POLICY: COLOMBIA

```{r MPfigure, echo=FALSE, warning=FALSE, results='asis', message=FALSE}
g <- ts(g, start=c(2002,1), frequency=12)
g <- window(g, start=c(2010,1))

plot(g, type='s', ylim=c(2, 9), yaxt='n', xaxt='n', ylab='', xlab='',
     lwd = 2, lty=1, bty='n', main='Key interest rate, Colombian Central Bank')  
rect(time(inflactual)[(200-113):(200-113)],
     1.5,
     time(inflactual)[108:108],
     9.5, density=50, col = "lightpink")
abline(h=c(3, 4, 5, 6, 7, 8), col='gray90')
abline(v = c(2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018), col='gray90')
axis(1, at = seq(2010, 2018, 1), tcl = 0.2)
axis(2, at = 1:10, las = 2, tcl = 0.5, labels = FALSE)
axis(4, at = 1:10, las = 2, tcl = 0.5)
lines(g, type='s')                          # línea tasa de intervención
# lines(ftaylor, type='s', lwd=5, col='black')      # predicción regla de taylor
box(col='dimgray')
```