\documentclass[11pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt} % Font size - 10pt, 11pt or 12pt
\usepackage[top=1in, bottom=1.25in, left=1.25in, right=1.25in]{geometry} % Document margins
\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box
\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors
\usepackage{tabularx}


% Colors for links, text and headings
%-----------------------------------------------------------------------
\usepackage{hyperref}
\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
\definecolor{shade}{HTML}{F0F6F7} % Peach color for the contact information box
\definecolor{text1}{HTML}{62797B} % Main document font color, off-black
\definecolor{headings}{HTML}{000066} % Dark red color for headings
% Other color palettes: shade=B9D7D9 and linkcolor=A40000; shade=D4D7FE and linkcolor=FF0080

\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors

\renewcommand{\headrulewidth}{0pt} % Get rid of the default rule in the header

\usepackage{titlesec} % Allows creating custom \section's

% Format of the section titles
\titleformat{\section}{\color{headings}
\scshape\large\raggedright}{}{0em}{}[\color{black}\titlerule]
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{datetime}
\setlength{\itemsep}{0.4cm} 
\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}

%==================================HEADERS AND FOOTERS=============================
\usepackage{fancyhdr}							          % Custom headers\pagestyle{fancy}		  					            
\pagestyle{fancy}
\usepackage{lastpage}	                      % page number
\lhead{}                                    % Header: left side empty
\chead{}                                    % Header: center side empty
\rhead{}                                    % Header: rigth side empty
\lfoot{\sffamily\footnotesize César Castro Rozo}   % Footer: left side
\cfoot{\sffamily\footnotesize June, 2021}                                    % Footer: center side empty
\rfoot{\sffamily\footnotesize \thepage}	% "Page 1 of 2"

% \renewcommand{\footrulewidth}{0.1pt}        % Footer: line
\fancypagestyle{firststyle}{\fancyhf{} \fancyfoot[R]{\footnotesize Page \thepage\ de \pageref{LastPage}} }
%============================================================================

\setlength{\parskip}{1em}            % paragraph separation
\onehalfspacing
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\par{
\centering{\color{gray}\sffamily\Huge César Castro Rozo}\\
\vspace{5pt}
{\scshape{June, 2021}}\\
\vspace{10pt}
}

\centering
\colorbox{shade}{{
\begin{tabular}{c|p{8cm}}
{\textifsymbol{18}} & \href{https://www.unavarra.es/departamento-economia}{Department of Economics}\\
& Universidad Pública de Navarra\\
& Campus Arrosadia, Madroño Building\\
\vspace{5pt}\raisebox{-4pt} & Pamplona, Spain 31006\\
\vspace{5pt}\raisebox{-4pt}{\Telefon} & Phone: (+34) 948 16 93 60\\
\vspace{5pt}\raisebox{-4pt}{\Letter} & Email: \href{mailto:cesar.castro@unavarra.es}{cesar.castro@unavarra.es} \\
\vspace{5pt}\raisebox{-4pt}{\Mundus} & Homepage: \href{https://cecarozo.github.io/cesar.castro}{https://cecarozo.github.io/cesar.castro}\\
\end{tabular}
}
}\\[10pt]
\vspace{10pt}

\raggedright
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\begin{itemize}
  \item {\textbf{Ph.D. in Economics} (Summa cum laude), Universidad de Salamanca, Spain
  Outstanding Doctorate Award.\\
  Dissertation title: Three Essays on Applied Time Series Econometrics.\\
  Advisor: Rebeca Jiménez-Rodríguez.\\
  Committee: Dolores Gadea (chair), Marcelo Sánchez, Gabriel Pérez Quirós.}
  \item \textbf{D.E.A. (Doctoral Studiesin Economics)}, Universidad de Alcalá, Spain.
  \item \textbf{M.A. in Economics}, Universidad Nacional de Colombia.
  \item \textbf{B.A. in Economics}, Universidad Nacional de Colombia.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Current Position} 

\textbf{Assistant Professor}, Department of Economics, Universidad Pública de Navarra (UPNA), Spain.\\

\vspace{10pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Previous Positions} 

\begin{itemize}
  \item \textbf{Assistant Researcher}, Instituto Flores de Lemus, Department of Statistics, Universidad Carlos III de Madrid, Spain.
  \item \textbf{Economist}, Macroeconomics Division, General Controller of Colombia.
  \item \textbf{Assistant Researcher}, Centro de Investigaciones para el Desarrollo, Department of Economics, Universidad Nacional de Colombia.
  \item \textbf{Lecturer}, Department of Economics, Universidad Nacional de Colombia.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Interests}

Time Series Econometrics, Empirical Macroeconomics, Energy Economics.\\

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\begin{itemize}
  \item \textbf{``Oil price pass-through into inflation in Spain at national and regional level''} with L. Topan (Universidad Complutense de Madrid), A. Barge-Gil (Universidad Complutense de Madrid), and M. Jerez (Universidad Complutense de Madrid). \emph{SERIEs}, 11(3), September 2020.
  \item \textbf{``Dynamic interactions between oil price and exchange rate''} with R. Jiménez-Rodríguez (Universidad de Salamanca). \emph{PLoS ONE}, 15(8), August 2020,  e0237172.
  \item \textbf{``Oil price pass-through along the price chain in the euro area''} with R. Jiménez-Rodríguez (Universidad de Salamanca). \emph{Energy Economics}, 64, May 2017, 24--30.
  \item \textbf{``A new look at oil price pass-through into inflation: Evidence from disaggregated European data''} with R. Jiménez-Rodríguez (Universidad de Salamanca), P. Poncela (JRC, European Commission), and E. Senra (Universidad de Alcalá). \emph{Economia Politica: Journal of Analytical and Institutional Economics}, 34(1), December 2016, 55--82.
  \item \textbf{``The deflationary effect of oil prices in the euro area''} with A. Barge-Gil (Universidad Complutense de Madrid), and M. Jerez (Universidad Complutense de Madrid). \emph{Energy Economics}, 56, May 2016, 389--397.
  \item \textbf{``Oil Prices and Inflation in the Euro Area and its Main Countries: Germany, France, Italy and Spain''} with P. Poncela (Universidad Autónoma de Madrid) and E. Senra (Universidad de Alcalá). \emph{FUNCAS Working papers series}, 701, December 2012.
  \item \textbf{``Do we see the effects of oil variations in official statistics price data?''} with P. Poncela (Universidad Autónoma de Madrid), and E. Senra (Universidad de Alcalá). \emph{Boletín de Estadística e Investigación Operativa}, 27, February 2011, 29--41.
  \item \textbf{``El diferencial de inflación en los servicios entre España y la euro área''} with E. Carluccio (Universidad Carlos III de Madrid). \emph{Papeles de Economía Española}, 120, June 2009, 69--89.
  \item \textbf{``Mercado de crédito 1990-1999. La factura de cobro del financiamiento''} with J. Espitia (General Controller of Colombia), and J. Villamizar (General Controller of Colombia). \emph{Gestión Fiscal}, 8, 2000, 6--33.
  \item \textbf{``La demanda de lotería y juegos de azar''} with J.I. González (Universidad Nacional de Colombia). \emph{INNOVAR, Revista de Ciencias Administrativas y Sociales}, 16, December 2000, 27--48.}
\end{itemize}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Projects}
\begin{itemize}
  \item \textbf{Design and application of economic models for institutional analysis.} Project leader: José E. Galdón. Research funding: Spanish Comission of Science PCG2018-093542-B-100. Spain, 2019--2021.
  \item \textbf{Dynamic econometric models, forecasts, economic outlook, inflation, macroeconomic models and time series.} Project leader: Antoni Espasa. Research funding: Universidad Carlos III de Madrid. Spain, 2010--2014.
  \item \textbf{Forecast and macroeconomic analysis. Inflation and relative prices in the region of Andalusia, Spain.} Project leader: Antoni Espasa. Research funding: Government of Andalusia. Spain, 2007--2009.
  \item \textbf{Analysis and forecasts of inflation.} Project leader: Antoni Espasa. Research funding: Universidad Carlos III de Madrid. Spain, 2006--2007.
  \item \textbf{Analysis and forecasts of inflation in the region of Madrid, Spain.} Project leader: Antoni Espasa. Research funding: Government of Madrid and Caja Madrid. Spain, 2002--2006.
  \item \textbf{Lottery demand.} Project leader: Jorge Iván González. Research funding: Lottery of Bogota. Colombia, 1999--2000.
  \item \textbf{Development plan in the region of Guavio, Colombia.} Project leader: César Castro. Research funding: Regional environment corporation, CORPOGUAVIO. Colombia, 1999--2000.
  \item \textbf{Environmental management in Colombian environmental ministry.} Project leader: César Castro. Research funding: Environmental ministry of Colombia. Colombia, 1999.
  \item \textbf{Economic impact of logging in indigenous area.} Project leader: César Castro. Research funding: Regional environment corporation, CODECHOCO. Colombia, 1997--1999.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conference and Seminar Presentations} 

\begin{itemize}
  \item \textbf{2019}\\
  44th Symposium Spanish Economic Association (SAEe), Alicante, Spain.\\
  II Workshop of the Spanish Macroeconomics Network, Barcelona, Spain.\\
  XX Conference on International Economics, Granada, Spain.
  \item \textbf{2018}\\
  Department of Economics, Universidad de Malaga, Spain.
  \item \textbf{2017}\\
  Department of Economics, Universidad Autónoma de Madrid, Spain.\\
  12th Conference of the Spanish Association for Energy Economics, Salamanca, Spain.
  \item \textbf{2016}\\
  7th Research Workshop on Energy Markets, Universidad de Valencia, Spain.\\
  Energy Economics Iberian Conference, Lisboa, Portugal.
  \item \textbf{2012} 32nd International Symposium on Forecasting, Boston, U.S.A.\\
  XXXIII Congreso Nacional de Estadística e Investigación Operativa, Madrid, Spain.
  \item \textbf{2011} Association of Southern European Economic Theorists, Évora, Portugal.\\
  Euro-Mediterranean Competitiveness Meeting, Universidad de Alcalá, Spain.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Referee} 

\raggedright
Energy Economics; Energy Sources, Part B: Economics, Planning, and Policy; The Energy Journal; Energies.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Teaching} 

\begin{itemize}
  \item Industrial Organization 2019 - present.
  \item Microeconomics 2019 -2020.
  \item Introduction to Economics 2019 - present.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Honors \& Awards} 

\begin{itemize}
  \item Profesor Ayudante Doctor by Agencia Nacional de Evaluacion de la Calidad y la Acreditación (ANECA).
  \item Universidad de Salamanca, Outstanding Doctorate Award.
  \item Santander Bank - Universidad de Alcalá, Scholarship.
  \item Inter-American Development Bank, Invited to the Youth and Growth Forum, Jerusalem, Israel.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Computer skills} 

\begin{itemize}
  \item \textbf{\textsf{R}} programming language
  \item {\LaTeX}
  \item \textsc{MATLAB}
\end{itemize}

\end{document}
